rotation_runs2019

### 2020-02-25 inst/documents/paper_figs_rotations201911.Rmd
finish past threshold change, bughunting and roxygen bumped. passes check

widthbin <- 10 #either 10 or 20 looks fairly similar

@@

>>>>

widthbin <- 10 #either 10 or 20 looks fairly similar, 5 gives gaps because of course runs are constrained to 1 year

@@

# 2020-02-25 checking B1 scenarios that are giving weird results
df_res_B1 <- dplyr::filter(df_res_16, idAD=='B' & id14 == 1)

df_res_B1 %>% group_by(gens_rot_minus_seq) %>% tally()
# A tibble: 7 x 2
#   gens_rot_minus_seq     n
#                <dbl> <int>
# 1                -10     1
# 2                  0  6454
# 3                 10  1653
# 4                 20  1207
# 5                 30   514
# 6                 40   150
# 7                 50    21
# so this seems to suggest that rotations are indeed better for B1

#possibilities :
#A something different in the runs that Sam did and the 200 example ones done for the document
#B a problem with the document

#but the B1 document looks as expected ???

# TODO 2020-02-25 check whats going on here

### 2020-02-25 inst/documents/rotation_runs2019.Rmd
finish past threshold change, bughunting and roxygen bumped. passes check

nscenarios <- 200
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
id_expt <- 'D4'

@@

  #record rotation rot interval locally otherwise it get soverwritten by 0
  rot_rot_interval <- linputs$rot_interval

>>>>

nscenarios <- 10
plotyn <- 1 #allow turning plots on and off from here, may want to turn plots off if doing large number of runs

# now specify an experiment from the multi-experiment file
#id_expt <- 'A1'
#id_expt <- 'A2'
#id_expt <- 'A3'
#id_expt <- 'A4'
id_expt <- 'B1'
#id_expt <- 'B2'
#id_expt <- 'B3'
#id_expt <- 'B4'
#id_expt <- 'C1'
#id_expt <- 'C4'
#id_expt <- 'D4'

@@

  #record rotation rot interval locally otherwise it gets overwritten by 0
  rot_rot_interval <- linputs$rot_interval

### 2020-02-25 inst/documents/rotations_notes.Rmd
finish past threshold change, bughunting and roxygen bumped. passes check

@@

>>>>

# 2020-02-25

checking on B1 runs following feedback from Sam.

B1 scenarios, (no costs, no dispersal, insecticides different).

In earlier runs there was no advantage to rotation when there is no cost and dispersal. In the latest runs there is.

I think this is something to do with time spent above the resistance threshold. You may remember that insecticides can only be changed on a yearly timestep. This can result in resistance going above threshold, when that happens it can result in simulations lasting longer.

It seems that something is happening with this that gives the advantage to rotations. This creates a slightly strange 'dog-tooth' pattern seen in fig x3 and pasted below.

But sam checked that in the example 200 runs there were just a few that had minor benefits for sequences (not rotations)

I could try doing 1000 runs to check ?
or do an equiv of fig x3 for the 200 runs.

its x2 which has the dogtooth
OR first check how the fig x2 is produced to check for possible glitches

fig x1 shows that of the runs that are different they mostly show benefit of rotation.

fig-si-1-abs-diff-rot-seq shows NO B1 runs with benefit of sequence.

# 2020-02-25 checking B1 scenarios that are giving weird results
df_res_B1 <- dplyr::filter(df_res_16, idAD=='B' & id14 == 1)

df_res_B1 %>% group_by(gens_rot_minus_seq) %>% tally()
# A tibble: 7 x 2
#   gens_rot_minus_seq     n
#                <dbl> <int>
# 1                -10     1
# 2                  0  6454
# 3                 10  1653
# 4                 20  1207
# 5                 30   514
# 6                 40   150
# 7                 50    21
# so this seems to suggest that rotations are indeed better for B1

#possibilities :
#A something different in the runs that Sam did and the 200 example ones done for the document
#B a problem with the document

#but the B1 document looks as expected ???

#should run 1,2,3 etc. from the doc be expected to be the same as the ones in df_res_B1 ?
#remember pdfs with figs are in C:\Dropbox\resistanceResults\rotations

#YES for run 1 the inputs look about the same
#EXCEPT that e.g. eff is recorded in df_res_B1 as just a single value (0.98) whereas there are 2 insecticides should be c(0.98,0.74)

#also starngely the pdf seems still to be showing gens in-use under thresh (maybe I didn't get around to changing that)

a) install-restart and try redoing B1 pdf for first 10 runs
1) check on changing gens-under-thresh output for pdf
2) check on saving multiple values when insecticides are diff

run1 
in pdf  rot:40, seq:40
in runs rot:50, seq:40

I wonder if something went wrong with Sams runs that just running 1 insecticide (but then would expect them to be just like A1 runs ??)

& maybe Sams reporting on the pdf was based on the gens-under-thresh numbers which are now superceded (my mistake for not updating package before re-running pdf)

Can I run the rot for run1 from the pdf, does it generate 40 as in the pdf or 50 as in the runs ?
eek maybe something hadn't updated before Sam did the runs ?

run_rot(rot_interval=10, n_insecticides=2, start_freqs=0.077, cost=c(0,0), eff=c(0.98,0.74), dom_sel=c(0.55,0.55),
dom_cos=c(0.24,0.76), rr=c(0.77,0.47), expo_hi=0.69, male_expo_prop=0.17, coverage=1, migration=0,
max_gen=500, change_interval=10)

this gives 40 gens, same as the pdf.

Now can I rerun the first 10 runs in the same way that Sam did ?
To do that can just click on the saved rda file.
It does give the same results as the pdf.

I think I may need to ask Sam to re-run. Making sure that we've updated everything.

One remaining query, why are the inputs for multiple insecticides not saved into the df_res_all object (by both mine & Sams runs) ?

it must happen here :
  df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq, 
                                        gens_u_rot=gens_u_rot, gens_u_seq=gens_u_seq,
                                        mort_rot=mort_rot, mort_seq=mort_seq, id=i))

linputs has the multiple entries for eff, df_in_out has lost them
i thought I had done something to allow for that in past ?

@@

2020-02-25 : probably get Sam to rerun the 16k runs
